---
title: "Differential Item Functioning By Language on the new PROMIS® Physical Functioning Items 2.0 for Adults"
subtitle: "1. EDA und Basic Psychometric Investigation"
author: "Constantin Yves Plessen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: show
    highlight: pygment
    keep_md: no
    theme: cerulean
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      collapse = FALSE,
                      cache = F,
                      comment = "",
                      strip.white = TRUE,
                      warning = FALSE, #we exclude warnings to improve readability
                      messages = FALSE,
                      out.width = "100%",
                      fig.width=6, 
                      fig.height=7,
                      fig.align = "center",
                      dpi = 200)

# Install and load correct package versions
if(!require(pacman)) install.packages("pacman")
pacman::p_install_version
pacman::p_load(tidyverse,
               officer,
               flextable,
               ggstatsplot,
               mirt,
               haven,
               lordif,
               readxl,
               arsenal,
               summarytools,
               raincloudplots,
               hrbrthemes,
               janitor,
               car,
               lavaan,
               semPlot,
               psych,
               nFactors,
               finalfit, questionr,
               MVN, tidyselect, psych, GPArotation,
               mokken, qgraph, lavaan, MBESS,
               ggridges, cowplot)
options(scipen = 999)

# Source functions
source("R/helper-functions.R")
```

# Data Wrangling

```{r}
load("data/data_complete.rda") 

str(data_complete)
glimpse(data_complete)
summary(data_complete)
```

<br>

# Exploratory Data Analysis

## Argentina 

```{r}
data_arg <- data_complete %>% 
  dplyr::filter(country == "arg")

print(dfSummary(data_arg, 
                varnumbers   = FALSE, 
                valid.col    = FALSE, 
                graph.magnif = 0.76),
      method = 'render')
```

<br>

## Germany 

```{r}
data_ger <- data_complete %>% 
  dplyr::filter(country == "ger")

print(dfSummary(data_ger, 
                varnumbers   = FALSE, 
                valid.col    = FALSE, 
                graph.magnif = 0.76),
      method = 'render')
```

<br>

## US

```{r}
data_usa <- data_complete %>% 
  dplyr::filter(country == "usa")

print(dfSummary(data_usa, 
                varnumbers   = FALSE, 
                valid.col    = FALSE, 
                graph.magnif = 0.76),
      method = 'render')
```

<br>

## Argentina, Germany, US

```{r results = 'asis'}
print(dfSummary(data_complete, 
                varnumbers   = FALSE, 
                valid.col    = FALSE, 
                graph.magnif = 0.76),
      method = 'render')
```

<br>



# Tables

## Table 1: Sociodemographics

```{r  results = "asis"}
options(qwraps2_markup = 'markdown')

summaryStructureSociodemographics <-
  list("Age" =
         list("min"       = ~ min(age, na.rm = TRUE),
              "max"       = ~ max(age, na.rm = TRUE),
              "mean (sd)" = ~ qwraps2::mean_sd(age, 
                                               na_rm = TRUE, 
                                               show_n = "never"),
              "median" = ~  median(age, na.rm = TRUE)),
       
       "Sex, female" =
         list(
           "N (%)"  = ~ qwraps2::n_perc0(gender == 2, na_rm = TRUE)),
       
       "Education" =
         list("Basic Education" = ~ qwraps2::n_perc0(edu_harmonized == "Basic Education",  na_rm = TRUE),
              "Secondary Education"  = ~ qwraps2::n_perc0(edu_harmonized == "Secondary Education",  na_rm = TRUE),
              "Vocational/Some College"  = ~ qwraps2::n_perc0(edu_harmonized == "Vocational/Some College",  na_rm = TRUE),
              "Higher Education" = ~ qwraps2::n_perc0(edu_harmonized == "Higher Education",  na_rm = TRUE))
       
       # "Work status" no information for USA
       
       # Marital status " no information for USA
  )
```


```{r  results = "asis"}
dataComplete <- data_complete %>% 
  mutate(country_table = dplyr::recode(country,  "usa" = "USA", "ger" = "Germany", "arg" = "Argentina"),
         country_table1 = factor(country_table, levels = c("USA", "Germany", "Argentina")))

summaryTableSociodemopgraphics <- qwraps2::summary_table(dplyr::group_by(dataComplete, country_table1), summaryStructureSociodemographics)

print(summaryTableSociodemopgraphics, rtitle = "Sociodemographics")
```

<br>

## Table 2: PROMIS
```{r  results = "asis"}
options(qwraps2_markup = 'markdown')

summaryStructurePROMIS <-
  list("PROMIS Physical Function T-Score" =
         list("min"       = ~ round(min(t_promis, na.rm = TRUE),2),
              "Floor (%)"  = ~ qwraps2::n_perc0(t_promis == min(t_promis), na_rm = TRUE),
              "max"       = ~ round(max(t_promis, na.rm = TRUE),2),
              "Ceiling (%)"  = ~ qwraps2::n_perc0(t_promis == max(t_promis), na_rm = TRUE),
              "IQR"       = ~ round(IQR(t_promis, na.rm = TRUE),2),
              "mean (sd)"  = ~ qwraps2::mean_sd(t_promis, 
                                                na_rm = TRUE, 
                                                show_n = "never"),
              "median" = ~  round(median(t_promis, na.rm = TRUE),2)
         ),
       "PROMIS Global Health - Physical Health" =
         list(#"min"       = ~ min(GLOBAL03, na.rm = TRUE),
           #"max"       = ~ max(GLOBAL03, na.rm = TRUE),
           #"IQR"       = ~ IQR(GLOBAL03, na.rm = TRUE),
           "mean (sd)"  = ~ qwraps2::mean_sd(global_health_physical_2a_t_score, 
                                             na_rm = TRUE, 
                                             show_n = "never"),
           "median" = ~  median(global_health_physical_2a_t_score, na.rm = TRUE)
         ), 
       "PROMIS Global Health - Mental Health" =
         list(#"min"       = ~ min(GLOBAL04, na.rm = TRUE),
           #"max"       = ~ max(GLOBAL04, na.rm = TRUE),
           #"IQR"       = ~ IQR(GLOBAL04, na.rm = TRUE),
           "mean (sd)"  = ~ qwraps2::mean_sd(global_health_mental_2a_t_score, 
                                             na_rm = TRUE, 
                                             show_n = "never"),
           "median" = ~  median(global_health_mental_2a_t_score, na.rm = TRUE)
         )#,
  )


summaryTable <- qwraps2::summary_table(dplyr::group_by(dataComplete, country_table1), summaryStructurePROMIS)

print(summaryTable, rtitle = "PROMIS Summary Statistics")
```


# Demographics
```{r}
#### Demographics, score distribution, and missing data frequency ####

# Dataset dimensions
dim(data_complete)
```

## Age
```{r}
data_complete %>%
  dplyr::select(age, country) %>%
  dplyr::group_by(country) %>%
  dplyr::summarize(
    mean_age = mean(age, na.rm = TRUE),
    median_age = median(age, na.rm = TRUE),
    min_age = min(age, na.rm = TRUE),
    max_age = max(age, na.rm = TRUE),
    n = n()  # Count of observations per group
  )
```


```{r}
data_complete %>% filter(age <= 69) %>%
  dplyr::select(age, country) %>%
  dplyr::group_by(country) %>%
  dplyr::summarize(
    mean_age = mean(age, na.rm = TRUE),
    median_age = median(age, na.rm = TRUE),
    min_age = min(age, na.rm = TRUE),
    max_age = max(age, na.rm = TRUE),
    n = n()  # Count of observations per group
  )
```


```{r}
ggplot(data_complete, aes(x = country, y = age, fill = country)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Age Distribution by Country", x = "Country", y = "Age") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

```

## Gender
```{r}
data_complete %>%
  dplyr::select(gender, country) %>%
  dplyr::group_by(country) %>%
  dplyr::summarize(
    female_percent = mean(gender-1, na.rm = TRUE) *100,
    n = n()  # Count of observations per group
  )

histo(data_complete, "gender")
```

## Country
```{r}
table(data_complete$country)
histo(data_complete, "country")
```


## Education
```{r}
table(data_complete$edu_harmonized)

histo(data_complete, "edu_harmonized")
```

## Employment
```{r}
summary(data_complete$employment)
table(data_complete$employment)
histo(data_complete, "employment")
```

## work_hrs

```{r}
summary(data_complete$work_hrs)
table(data_complete$work_hrs)
histo(data_complete, "work_hrs")
```

## household_size_t1

```{r}
table(data_complete$household_size_t1)
histo(data_complete, "household_size_t1")
```

## household_size_t2
```{r}
table(data_complete$household_size_t2)
histo(data_complete, "household_size_t2")
```

## GL03-06
```{r}
summary(data_complete$GL03)
table(data_complete$GL03)
histo(data_complete, "GL03")

# GL04
table(data_complete$GL04)
histo(data_complete, "GL04")

# GL05
table(data_complete$GL05)
histo(data_complete, "GL05")

# GL06
table(data_complete$GL06)
histo(data_complete, "GL06")
```

<br>

# Inspect T-Scores and Item Responses

## Figure T-score distribution and item responses
```{r}
grouping_vector <- c("usa", "ger", "arg")
items <- filter_items(data_complete, 
                      countries = grouping_vector)

data_viz <- data_complete %>% 
  mutate(country = case_match(country,
                              "arg" ~ "Argentina", 
                              "usa" ~ "USA", 
                              "ger" ~ "Germany")) %>% 
  dplyr::select(
    country,
    country_vector,
    age,
    names(items),
    t_promis)

data_viz_long <- data_viz %>% 
  pivot_longer(cols = PFM1:PFM53,
               names_to = "item")
```

### Item Response Plot
```{r}
item_responses <- data_viz_long %>% 
  ggplot(
    
    aes(x=factor(item,
                 levels = rev(c("PFM1", "PFM2", "PFM3", "PFM4", "PFM6", "PFM7", "PFM9", "PFM10", 
                                "PFM12", "PFM15", "PFM16", "PFM17", "PFM18", "PFM19", "PFM21", 
                                "PFM23", "PFM25", "PFM26", "PFM27", "PFM28", "PFM29", "PFM32", 
                                "PFM33", "PFM34", "PFM35", "PFM36", "PFM37", "PFM38", "PFM40", 
                                "PFM43", "PFM44", "PFM46", "PFM49", "PFM51", "PFM53"))))) +
  geom_bar(aes(fill=rev(as.factor(value))), position="fill") +
  
  scale_y_continuous(expand=expansion(0), labels=scales::percent_format()) +
  labs(
    title='Item Responses', 
    subtitle='PROMIS Physical Functioning',
    x='Items', 
    y='% Responses'
  ) +
  scale_fill_brewer(name = "", 
                    labels = c("Unable", 
                               "Much Difficulty", 
                               "Some Difficulty", 
                               "Little Difficulty",
                               "No Difficulty"),
                    palette='Spectral', 
                    direction=1) +
  theme_classic()+
  theme(legend.position='top') + 
  guides(fill = guide_legend(reverse=TRUE)) +
  facet_wrap(~country) + 
  coord_flip() +
  theme(
    # This is the new default font in the plot
    text = element_text(
      #family = "Arial", 
      size = 8, color = "black"),
    plot.title = element_text(
      #family = "Arial", 
      size = 15,
      face = "bold",
      color = "#2a475e"
    ),
    # Statistical annotations below the main title
    plot.subtitle = element_text(
      #family = "Arial", 
      size = 10, 
      face = "bold",
      color="#1b2838"
    ),
    plot.title.position = "plot", # slightly different from default
    axis.text = element_text(size = 10, color = "black"),
    axis.title = element_text(size = 12)
  ) +
  theme(
    axis.ticks = element_blank(),
    axis.line = element_line(colour = "grey50"),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(linetype = "dashed")
  )
```

### Distribution of T-Scores
```{r}

# Calculate median for each country
medians <- data_viz %>%
  group_by(country) %>%
  dplyr::summarize(median_t_promis = median(t_promis)) 

# Initialize an empty data frame to store density at medians
density_at_medians <- data.frame(country = character(), median_t_promis = numeric(), density = numeric())

# Calculate the density at these median points for each country
for (country_name in unique(data_viz$country)) {
  data_country <- data_viz[data_viz$country == country_name, ]
  density_obj <- density(data_country$t_promis)
  
  median_val <- medians$median_t_promis[medians$country == country_name]
  median_density <- approx(density_obj$x, density_obj$y, xout = median_val)$y
  
  density_at_medians <- rbind(density_at_medians, data.frame(country = country_name, median_t_promis = median_val, density = median_density))
}
# Find the range of your data
data_range <- range(data_viz$t_promis, na.rm = TRUE)

# Plotting
distribution_plot <- data_viz %>%
  ggplot(aes(x = t_promis, group = country)) +
  geom_density(aes(color = country, linetype = country), alpha = 0.6, adjust = 1) +  # adjust parameter controls smoothness
  geom_segment(data = density_at_medians, aes(x = median_t_promis, xend = median_t_promis, y = 0, yend = density, color = country), linetype = "dashed") +
  scale_color_manual(values = c("USA" = "black", "Argentina" = "green", "Germany" = "red")) +
  scale_linetype_manual(values = c("USA" = "solid", "Argentina" = "dotted", "Germany" = "dashed")) +
  viridis::scale_fill_viridis(discrete = TRUE) +
  scale_x_continuous(breaks = c(20, 30, 40, 50, 60, 70, 80), limits = c(data_range[1] - 10, data_range[2] + 10)) +  # Extend the x-axis limits
  labs(
    x = 'T-scores',
    y = 'Density',
    title = 'Distribution of PROMIS Physical Function T-Scores',
    color = "Country",
    linetype = "Country"
  ) +
  guides(
    #linetype = guide_legend(title = NULL)  # Uncomment this to remove linetype legend title
  ) +
  theme_classic() +
  theme(
    panel.border = element_rect(color = "black", fill = NA, linewidth = 1),
    panel.background = element_blank(),
    axis.line = element_line(color = "black"),
    legend.position = c(.999, .999),
    legend.justification = c("right", "top"),
    legend.background = element_rect(color = "black", fill = "white", size = 0.5),
    legend.box.background = element_blank(),
    legend.box.margin = margin(0, 0, 0, 0)
  )
```


```{r}
ggstatsplot::ggbetweenstats(
  data = data_viz,
  x = country,
  y = t_promis,
  p.adjust.method = "bonferroni",
  pairwise.display = "all",
  type = "nonparametric"
) 
```


### Distribution of T-Scores including stats
```{r}
plot_t_scores <-  ggstatsplot::ggbetweenstats(
  data = data_viz,
  x = country,
  y = t_promis,
  p.adjust.method = "bonferroni",
  pairwise.display = "all",
  type = "nonparametric"
) + 
  # Add labels and title
  labs(
    x = "Country",
    y = "PROMIS Ceiling Physical Function Items",
    title = "Distribution of PROMIS Ceiling Physical Function T-Scores"
  ) + 
  # Customizations
  theme(
    # This is the new default font in the plot
    text = element_text(family = "Roboto", size = 8, color = "black"),
    plot.title = element_text(
      family = "Roboto", 
      size = 15,
      face = "bold",
      color = "#2a475e"
    ),
    # Statistical annotations below the main title
    plot.subtitle = element_text(
      family = "Roboto", 
      size = 10, 
      face = "bold",
      color="#1b2838"
    ),
    plot.title.position = "plot", # slightly different from default
    axis.text = element_text(size = 10, color = "black"),
    axis.title = element_text(size = 12)
  ) +
  theme(
    axis.ticks = element_blank(),
    axis.line = element_line(colour = "grey50"),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(linetype = "dashed")
  )

plot_t_scores
```

### Combine plots
```{r}
plot_item_responses <- cowplot::plot_grid(plot_t_scores, item_responses, ncol = 1)
plot_item_responses
```

