---
title: "Differential Item Functioning By Language on the new PROMIS® Physical Functioning Items 2.0 for Adults"
subtitile: "3.1 Influence of Flagged DIF Items at the Item Level "
author: "Constantin Yves Plessen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
knit: (function(inputFile, encoding) {
      rmarkdown::render(inputFile, 
      encoding = encoding, 
      output_dir = "vignettes") })
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: show
    highlight: pygment
    keep_md: no
    theme: cerulean
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      collapse = FALSE,
                      comment = "",
                      strip.white = TRUE,
                      warning = FALSE, #we exclude warnings to improve readability
                      messages = FALSE,
                      lwd = 2,
                      out.width = "100%",
                      fig.width=8, 
                      fig.height=8,
                      fig.align = "center",
                      dpi = 300)

library(tidyverse)
library(gridExtra)
library(cowplot)
library(readxl)

options(scipen = 999)
```


# Load and clean data

- Load data including all specifications from previous step.
- Indicate if item was flagged = 1 or was not flagged = 0

```{r}
all_specifications <- read.csv("data/specification_results.csv") %>% 
  dplyr::mutate(row = row_number(),
                hf_2_parameter = hf_2_parameter_vector )   %>% 
  
  # Indicate if item was flagged = 1 or was not flagged = 0
  separate_rows(Flagged_items, sep = "-") %>%
  mutate(value = 1) %>%
  spread(Flagged_items, value, fill = 0) %>% # Creates automatically V1 indicating where no Items were flagged
  # Combine criterion and threshold into variable hf_3_criterion
  mutate(hf_3_criterion = paste0(hf_3_criterion, ": ", hf_4_threshold)) %>% 
  dplyr::select(-c(X)) %>% 
  
  # create overall method variable
  mutate(method = case_when(
    str_detect(hf_3_criterion, "Cox") ~ "R2 Cox",
    str_detect(hf_3_criterion, "McFadden") ~ "R2 McFadden",
    str_detect(hf_3_criterion, "Nagelkerke") ~ "R2 Nagelkerke",
    str_detect(hf_3_criterion, "beta") ~ "beta",
    str_detect(hf_3_criterion, "lr") ~ "lr",
    TRUE ~ "other" #
  )) 
```

## Choose Specifications

Create data sets that have either all specifications, no LR analyses, or only LR analyses.
```{r}
nolr_specifications <- all_specifications %>% 
  filter(method != "lr") %>% 
  dplyr::select(-row) %>%
  distinct()

specifications_only_lr <- all_specifications %>% 
  filter(method == "lr")

specifications <- all_specifications
```

## Create Vector with Ceiling items
```{r}
pf_items <- c("PFM1", "PFM2", "PFM3", "PFM4", "PFM6", "PFM7", "PFM9", "PFM10", 
              "PFM12", "PFM15", "PFM16", "PFM17", "PFM18", "PFM19", "PFM21", 
              "PFM23", "PFM25", "PFM26", "PFM27", "PFM28", "PFM29", "PFM32", 
              "PFM33", "PFM34", "PFM35", "PFM36", "PFM37", "PFM38", "PFM40", 
              "PFM43", "PFM44", "PFM46", "PFM49", "PFM51", "PFM53")
```

<br>

# Figure: Item Specific Despriptive Specification Plot

## Preparation

<br>

### Which factors

```{r}
wf_1_comparison_vec <- unique(specifications$wf_1_comparison)
```

### How Factors

```{r}
hf_1_correction_vec <- unique(specifications$hf_1_correction)
hf_2_parameter_vec <- unique(specifications$hf_2_parameter)
vec <- unique(nolr_specifications$hf_3_criterion)
hf_3_criterion_vec <- vec[order(
  sub(":.*", "", vec) != "beta",
  sub(":.*", "", vec) != "CoxSnell",
  sub(":.*", "", vec) != "McFadden",
  sub(":.*", "", vec) != "Nagelkerke",
  sub(":.*", "", vec),
  as.numeric(sub(".*:", "", vec))
)]

number_which_how_factors <- 4

ylabels <- rev(c(
  "Comparison: USA-GER-ARG",  
  "Comparison: USA-GER",
  "Comparison: USA-ARG", 
  "Comparison: GER-ARG",
  
  "Correction: For Age",  
  "Correction: None",  
  
  "Parameters: Estimated", 
  "Parameters: PROMIS",
  
  "Criterion: Beta: 0.05",
  "Criterion: Beta: 0.10",
  
  "Criterion: Cox-Snell: 0.02",
  "Criterion: Cox-Snell: 0.03",
  "Criterion: Cox-Snell: 0.05",
  "Criterion: McFadden: 0.02",
  "Criterion: McFadden: 0.03",
  "Criterion: McFadden: 0.05",
  "Criterion: Nagelkerke: 0.02",
  "Criterion: Nagelkerke: 0.03",
  "Criterion: Nagelkerke: 0.05"#,
# "Comparison: USA-GER-ARG (1.5%)",  
# "Comparison: USA-GER (0.1%)",
# "Comparison: USA-ARG (1.1%)", 
# "Comparison: GER-ARG (2.2%)",
# 
# "Correction: For Age (2.0%)",  
# "Correction: None (2.8%)",  
# 
# "Parameters: Estimated (2.4%)", 
# "Parameters: PROMIS (2.4%)",
# 
# "Criterion: Beta: 0.05 (0.9%)",
# "Criterion: Beta: 0.10 (0.4%)",
# 
# "Criterion: Cox-Snell: 0.02 (0.8%)",
# "Criterion: Cox-Snell: 0.03 (0.6%)",
# "Criterion: Cox-Snell: 0.05 (0.4%)",
# "Criterion: McFadden: 0.02 (0.5%)",
# "Criterion: McFadden: 0.03 (0.4%)",
# "Criterion: McFadden: 0.05 (0.1%)",
# "Criterion: Nagelkerke: 0.02 (0.4%)",
# "Criterion: Nagelkerke: 0.03 (0.3%)",
# "Criterion: Nagelkerke: 0.05 (0.1%)"#,
# 
  #"Criterion: LR: 1%",
  #"Criterion: LR: 5%",
  #"Criterion: LR Benjamini-Hochberg: 1%",
  #"Criterion: LR Benjamini-Hochberg: 5%",
  #"Criterion: LR Bonferroni: 1%",
  #"Criterion: LR Bonferroni: 5%"
))

# colors for flagged items
cols <- c("orange",
          "purple")

# vector needed for plotting
length_of_each_factor <- c(
  length(hf_3_criterion_vec),
  length(hf_2_parameter_vec) +  length(hf_3_criterion_vec) ,
  length(hf_1_correction_vec) +   length(hf_2_parameter_vec) +  length(hf_3_criterion_vec),
  length(wf_1_comparison_vec) +   length(hf_1_correction_vec) +   length(hf_2_parameter_vec) +  length(hf_3_criterion_vec))
```

## `create_tile_plot()`

```{r}
create_tile_plot <- function(specifications, pf_item) {
  
  x_rank <- rank(specifications[[pf_item]],  
                 ties.method = "random")
  
  ### Create all factors
  yvar <- rep(factor(rev(c(
    wf_1_comparison_vec,
    hf_1_correction_vec,
    hf_2_parameter_vec,
    hf_3_criterion_vec)), 
    levels = rev(c(
      wf_1_comparison_vec,
      hf_1_correction_vec,
      hf_2_parameter_vec,
      hf_3_criterion_vec))), 
    times = nrow(specifications))
  
  xvar <- rep(x_rank, 
              each = length(levels(yvar)))
  
  flagged <- rep(specifications[[pf_item]],
                 each = length(levels(yvar)))
  spec <- NULL
  
  for(i in 1:nrow(specifications)) {
    id <- as.numeric(levels(yvar) %in% 
                       as.character(unlist(
                         specifications[i, 1:number_which_how_factors])))  
    spec <- c(spec, id)
  }
  
  plotdata <- data.frame(xvar, 
                         yvar, 
                         spec,
                         flagged) %>% 
    mutate(fill = ifelse(spec == 1 & flagged == 1, 2, ifelse(spec == 1 & flagged == 0, 1, 0)))
  
  
  tile_plot <- ggplot(data = plotdata, 
                      aes(x = xvar, 
                          y = as.factor(yvar), 
                          fill = factor(fill))) +
    geom_raster() + 
    geom_hline(yintercept = length_of_each_factor + 0.5) +  # Change lines here here
    scale_x_continuous(position = "bottom") +
    scale_y_discrete(labels = ylabels) +
    scale_fill_manual(
      values = c("white", cols)) +
    labs(x = "Specification number", 
         y = "Which/How factors") +
    coord_cartesian(
      expand = F, 
      xlim = c(0.5, nrow(specifications) + 0.5)) +
    theme_bw() + 
    theme(legend.position = "none",
          axis.text.y = element_text(colour = "black", size = 8),
          axis.text.x = element_text(colour = "black"),
          axis.ticks = element_line(colour = "black"),
          plot.margin = margin(t = 5.5, 
                               r = 5.5, 
                               b = 5.5, 
                               l = 5.5, 
                               unit = "pt"))
  return(tile_plot)
}
```

```{r}
create_tile_plot(specifications, "PFM46")
create_tile_plot(nolr_specifications, "PFM46")

```



## `create_flag_plot()`
```{r}
create_flag_plot <- function(specifications, pfm) {
  
  specifications$xvar <- rank(specifications[[pfm]],  
                              ties.method = "random")
  # Create a ggplot for the specified PFM item
  ggplot_spec <- ggplot(specifications, aes(x = xvar, 
                                            y = as.numeric(.data[[pfm]] == 1),
                                            fill = factor(.data[[pfm]]))) +
    geom_tile(aes(width = 1, height = 1)) +
    scale_fill_manual(values = cols) +
    labs(x = "", y = NULL, title = "") +
    guides(fill = FALSE) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    theme_void()
  
  # Return the ggplot object
  return(ggplot_spec)
}
```


## Combine Plots

```{r}
# Loop over each PFM item
for (pfm in pf_items) {
  # Create the flagged plot
  flagged_plot <- create_flag_plot(nolr_specifications, pfm)
  
  # Create the tile plot
  tile_plot <- create_tile_plot(nolr_specifications, pfm)
  
  # Create the grid of plots
  plot_grid <- plot_grid(
    flagged_plot,
    tile_plot,
    labels = c(pfm, ""),
    ncol = 1,
    align = "v",
    rel_heights = c(0.5, 5)
  )
  
plot_grid
}

```

# Figure: Descriptive Specification Plot

## Only Flagged Items

### Flagged Plot
```{r}
# Create a list to hold the flagged plots for each PFM item
flagged_plots <- list()

# Loop over the PFM items and create a flagged plot for each one
for (pfm in pf_items) {
  flagged_plots[[pfm]] <- create_flag_plot(nolr_specifications, pfm)
}

# Combine all the flagged plots into a grid of plots in one column
flagged_grid <- plot_grid(plotlist = flagged_plots, 
                          labels = pf_items,
                          label_size = 8,
                          ncol = 1)

# Display the grid of plots
flagged_grid
```


### Tile Plot
```{r}
specifications_long <- specifications  %>% 
  pivot_longer(cols = PFM1:PFM9,
               names_to = "item") %>% filter(value == 1)

yvar <- rep(factor(rev(c(
  wf_1_comparison_vec,
  hf_1_correction_vec,
  hf_2_parameter_vec,
  hf_3_criterion_vec)), 
  levels = rev(c(
    wf_1_comparison_vec,
    hf_1_correction_vec,
    hf_2_parameter_vec,
    hf_3_criterion_vec))), 
  times = nrow(specifications_long))

#### Rank each summary effect size by magnitude

x_rank <- rank(specifications_long$value, 
               ties.method = "random")

flagged <- rep(specifications_long$value, 
               each = length(levels(yvar)))
spec <- NULL

#### Determine which specifications are observed and which are not

for(i in 1:nrow(specifications_long)) {
  id <- as.numeric(levels(yvar) %in% 
                     as.character(unlist(
                       specifications_long[i, 1:number_which_how_factors])))  
  spec <- c(spec, id)
}

xvar <- rep(x_rank, 
            each = length(levels(yvar)))

plotdata <- data.frame(xvar, 
                       yvar, 
                       spec,
                       flagged)


# Generate a color palette
num_colors <- length(unique(plotdata$xvar))
colors <- colorRampPalette(c("blue", "purple", "orange"))(num_colors)

# Map each unique xvar to a color
color_map <- setNames(colors, unique(plotdata$xvar))


plotdata <- plotdata %>% 
  mutate(fill = ifelse(spec == 1 & flagged == 1, 2, ifelse(spec == 1 & flagged == 0, 1, 0)))

tile_plot_all_items <- ggplot(data = plotdata, 
                              aes(x = xvar, 
                                  y = as.factor(yvar), 
                                  fill = factor(fill))) +
  geom_raster() + 
  geom_hline(yintercept = length_of_each_factor + 0.5) +  # Change lines here here
  scale_x_continuous(position = "bottom") +
  scale_y_discrete(labels = ylabels) +
  scale_fill_manual(values = c("white", "orange")) +
  labs(x = "Specification number", 
       y = "Which/How factors") +
  coord_cartesian(
    expand = F, 
    xlim = c(0.5, nrow(specifications_long) + 0.5)) +
  theme_bw() + 
  theme(legend.position = "none",
        axis.text.y = element_text(colour = "black", size = 8),
        axis.text.x = element_text(colour = "black"),
        axis.ticks = element_line(colour = "black"),
        plot.margin = margin(t = 5.5, 
                             r = 5.5, 
                             b = 5.5, 
                             l = 5.5, 
                             unit = "pt"))

tile_plot_all_items
```


## All Items
```{r}
specifications_long <- specifications  %>% 
  pivot_longer(cols = PFM1:PFM9,
               names_to = "item") 

yvar <- rep(factor(rev(c(
  wf_1_comparison_vec,
  hf_1_correction_vec,
  hf_2_parameter_vec,
  hf_3_criterion_vec)), 
  levels = rev(c(
    wf_1_comparison_vec,
    hf_1_correction_vec,
    hf_2_parameter_vec,
    hf_3_criterion_vec))), 
  times = nrow(specifications_long))

#### Rank each summary effect size by magnitude

x_rank <- rank(specifications_long$value, 
               ties.method = "random")

flagged <- rep(specifications_long$value, 
               each = length(levels(yvar)))
spec <- NULL

#### Determine which specifications are observed and which are not

for(i in 1:nrow(specifications_long)) {
  id <- as.numeric(levels(yvar) %in% 
                     as.character(unlist(
                       specifications_long[i, 1:number_which_how_factors])))  
  spec <- c(spec, id)
}

xvar <- rep(x_rank, 
            each = length(levels(yvar)))

plotdata <- data.frame(xvar, 
                       yvar, 
                       spec,
                       flagged)


plotdata <- plotdata %>% 
  mutate(fill = ifelse(spec == 1 & flagged == 1, 2, ifelse(spec == 1 & flagged == 0, 1, 0)))
```

### Universe tile plot

```{r}
tile_plot_all_items <- ggplot(data = plotdata, 
                              aes(x = xvar, 
                                  y = as.factor(yvar), 
                                  fill = factor(fill))) +
  geom_raster() + 
  geom_hline(yintercept = length_of_each_factor + 0.5) +  # Change lines here here
  scale_x_continuous(position = "bottom") +
  scale_y_discrete(labels = ylabels) +
  scale_fill_manual(
    values = c("white", cols)) +
  labs(x = "Specification number", 
       y = "Which/How factors") +
  coord_cartesian(
    expand = F, 
    xlim = c(0.5, nrow(specifications_long) + 0.5)) +
  theme_bw() + 
  theme(legend.position = "none",
        axis.text.y = element_text(colour = "black", size = 8),
        axis.text.x = element_text(colour = "black"),
        axis.ticks = element_line(colour = "black"),
        plot.margin = margin(t = 5.5, 
                             r = 5.5, 
                             b = 5.5, 
                             l = 5.5, 
                             unit = "pt"))
tile_plot_all_items
```


# Tables

## Overall Flagged Items

### All Analyses

```{r}
result_overall_all <- all_specifications %>%
  dplyr::summarise(across(contains("PF"), sum, .names = "{.col}")) %>%
  pivot_longer(cols = everything(), names_to = "variable", values_to = "sum") %>% 
  mutate(percent = round(sum/nrow(all_specifications)*100, 1)) %>% arrange(desc(percent))

print(result_overall_all) 

# 5 most flagged items
print(result_overall_all) %>% slice(1:5) %>% pull(variable)

# Percentage of flagged items
result_overall_all %>% 
  summarise(sum = sum(sum)) %>% 
  mutate(percent_flagged = sum / (nrow(all_specifications)*35) *100) 
```

### Only LR
```{r}
result_overall_lr <- specifications_only_lr %>%
  dplyr::summarise(across(contains("PF"), sum, .names = "{.col}")) %>%
  pivot_longer(cols = everything(), names_to = "variable", values_to = "sum") %>% 
  mutate(percent = sum/nrow(specifications)*100) %>% 
  arrange(desc(percent))

print(result_overall_lr) 

# 5 most flagged items
print(result_overall_lr) %>% slice(1:5) %>% pull(variable)

# Percentage of flagged items
result_overall_lr %>% summarise(sum = sum(sum)) %>% 
  mutate(percent_flagged = sum / (nrow(specifications_only_lr)*35) *100)
```

### No LR

```{r}
result_overall <- nolr_specifications %>%
  dplyr::summarise(across(contains("PF"), sum, .names = "{.col}")) %>%
  pivot_longer(cols = everything(), names_to = "variable", values_to = "sum") %>% 
  mutate(percent = round(sum/nrow(specifications)*100, 1)) %>% arrange(desc(percent))

print(result_overall) 

# 5 most flagged items
print(result_overall) %>% slice(1:5) %>% pull(variable)

# Percentage of flagged items
result_overall %>% 
  summarise(sum = sum(sum)) %>% 
  mutate(percent_flagged = sum / (nrow(nolr_specifications)*35) *100) 

```

```{r}
data_items_ger <-  read_excel("data/tidy/items_ao2.xlsx", sheet = 3)

data_items_eng <- read_excel("data/tidy/items_ao2.xlsx", sheet = 1) %>% 
  filter(id %in% data_items_ger$id)

data_items_eng %>% left_join(result_overall, by = c("id" = "variable")) %>% drop_na(sum) %>% 
  dplyr::select(`PROMIS Item` = id,
                `Item Stem` = item,
                # `Response Categories` = response,
                `k` = sum,
                Percent = percent)
```



## At least X flagged item(s)
```{r}
nolr_specifications %>% filter(k_flagged>=1) %>% nrow() / nrow(nolr_specifications)*100
nolr_specifications %>% filter(k_flagged>=2) %>% nrow() / nrow(nolr_specifications)*100
nolr_specifications %>% filter(k_flagged>=3) %>% nrow() / nrow(nolr_specifications)*100
nolr_specifications %>% filter(k_flagged>=4) %>% nrow() / nrow(nolr_specifications)*100
nolr_specifications %>% filter(k_flagged>=5) %>% nrow() / nrow(nolr_specifications)*100
nolr_specifications %>% filter(k_flagged>=6) %>% nrow() / nrow(nolr_specifications)*100
nolr_specifications %>% filter(k_flagged>=7) %>% nrow() / nrow(nolr_specifications)*100
nolr_specifications %>% filter(k_flagged>=8) %>% nrow() / nrow(nolr_specifications)*100
nolr_specifications %>% filter(k_flagged>=9) %>% nrow() / nrow(nolr_specifications)*100
nolr_specifications %>% filter(k_flagged>=10) %>% nrow() / nrow(nolr_specifications)*100
```


```{r}
nolr_specifications %>% arrange(desc(k_flagged)) 
```

1. Item `r result_overall$variable[1]` was flagged for DIF in `r round(result_overall$percent[1], 1)`% of all analyses conducted.

2. In `r round(result_overall$percent[2], 1)`% of the analyses performed, item `r result_overall$variable[2]` was flagged.

3. `r round(result_overall$percent[3], 1)`% of all conducted analyses indicated a flag for item `r result_overall$variable[3]`.

4. The analysis flagged item `r result_overall$variable[4]` in `r round(result_overall$percent[4], 1)`% of the cases.

5. Throughout all analyses, item `r result_overall$variable[5]` was flagged in `r round(result_overall$percent[5], 1)`% of them.

<br>

## create_flagged_item_table()

Function that takes the specification data and creates summary tables of flagged items
```{r}
create_flagged_item_level_table <- function(data, variable) {
  data %>%
    dplyr::group_by({{variable}}) %>%
    dplyr::summarise(across(contains("PF"), sum, .names = "{.col}")) %>%
    pivot_longer(cols = -{{variable}}, names_to = "variable", values_to = "sum") %>% 
    dplyr::mutate(percent = sum/nrow(data)*100) %>% 
    dplyr::arrange(desc(sum)) 
}

create_flagged_item_table <- function(data, variable) {
  data %>%
    dplyr::group_by({{variable}}) %>%
    dplyr::summarise(across(contains("PF"), sum, .names = "{.col}")) %>%
    pivot_longer(cols = -{{variable}}, names_to = "variable", values_to = "sum") %>% 
    dplyr::mutate(percent = sum/nrow(data)*100) %>% 
    dplyr::arrange(desc(sum)) %>% 
    dplyr::group_by({{variable}})%>% 
    dplyr::summarise(sum = sum(sum)) %>% 
    dplyr::mutate(percent_flagged = sum / (nrow(data)*35) *100)
}
```

```{r}
Nagelkerke <- c("Nagelkerke: 0.05", "Nagelkerke: 0.03", "Nagelkerke: 0.02")
CoxSnell <- c("CoxSnell: 0.05", "CoxSnell: 0.03", "CoxSnell: 0.02")
McFadden <- c("McFadden: 0.05", "McFadden: 0.03", "McFadden: 0.02")
beta <- c("beta: 0.1", "beta: 0.05")
method <- c(Nagelkerke, CoxSnell, McFadden, beta)
correction <- c("no", "age")
parameters <- c("parameters_promis", "parameters_multigroup")
country <- c("ger-arg", "usa-arg", "usa-ger", "usa-ger-arg")
```

## By wf_1_comparison

```{r}
all_specifications %>%
    dplyr::group_by(wf_1_comparison) %>%
    dplyr::summarise(across(contains("PF"), sum, .names = "{.col}")) %>%
    pivot_longer(cols = -wf_1_comparison, names_to = "variable", values_to = "sum") %>% 
    dplyr::mutate(percent = sum/(nrow(all_specifications)/4)*100)
```

In all analyses for ger-arg, 27.85% of items were flagged for dif
```{r}
all_specifications %>%
    dplyr::group_by(wf_1_comparison) %>%
    dplyr::summarise(across(contains("PF"), sum, .names = "{.col}")) %>%
    pivot_longer(cols = -wf_1_comparison, names_to = "variable", values_to = "sum") %>% 
    dplyr::mutate(percent = sum/nrow(all_specifications)*100) %>% 
    dplyr::arrange(wf_1_comparison)  %>% 
    dplyr::group_by(wf_1_comparison)%>% 
    dplyr::summarise(sum = sum(sum)) %>% 
    dplyr::mutate(percent_flagged = sum / (nrow(all_specifications)*35/4) *100)
```
much better denominator: in all analyses for wf_1_comparison = ger-arg, PFM1 was flagged 30.8 percent of the time
```{r}
nolr_specifications %>%
    dplyr::group_by(wf_1_comparison) %>%
    dplyr::summarise(across(contains("PF"), sum, .names = "{.col}")) %>%
    pivot_longer(cols = -wf_1_comparison, names_to = "variable", values_to = "sum") %>% 
    dplyr::mutate(percent = sum/(nrow(all_specifications)/4)*100)
```

In all analyses for ger-arg, 27.85% of items were flagged for dif
```{r}
nolr_specifications %>%
    dplyr::group_by(wf_1_comparison) %>%
    dplyr::summarise(across(contains("PF"), sum, .names = "{.col}")) %>%
    pivot_longer(cols = -wf_1_comparison, names_to = "variable", values_to = "sum") %>% 
    dplyr::mutate(percent = sum/nrow(all_specifications)*100) %>% 
    dplyr::arrange(wf_1_comparison)  %>% 
    dplyr::group_by(wf_1_comparison)%>% 
    dplyr::summarise(sum = sum(sum)) %>% 
    dplyr::mutate(percent_flagged = sum / (nrow(all_specifications)*35/4) *100)
```


### All Specifications
```{r}
result_wf1_all <- create_flagged_item_table(all_specifications, wf_1_comparison)
result_wf1_all

create_flagged_item_level_table(all_specifications, wf_1_comparison)
```

### Specifications without LR
```{r}
result_wf1_nolr <- create_flagged_item_table(nolr_specifications, wf_1_comparison)
result_wf1_nolr

create_flagged_item_level_table(nolr_specifications, wf_1_comparison)
```

### Double check with alternative process
```{r}
plotdata %>% 
  filter(yvar %in% country) %>% 
  group_by(yvar) %>% 
  dplyr::summarise(times_flagged = sum(fill ==2))  %>% 
  mutate(percent = times_flagged / (length(unique(plotdata$xvar)))*100)
```

### Text
```{r}
result_wf1 <- result_wf1_all
```

For the comparison between `r result_wf1$wf_1_comparison[1]`, `r round(result_wf1$percent_flagged[1], 1)`% of all items were flagged for DIF. 

Comparing `r result_wf1$wf_1_comparison[2]`, we found that `r round(result_wf1$percent_flagged[2], 1)`% of the total items were indicated for DIF.

When comparing `r result_wf1$wf_1_comparison[3]`, `r round(result_wf1$percent_flagged[3], 1)`% of all items were flagged for DIF.

Comparing `r result_wf1$wf_1_comparison[4]`, it was noted that `r round(result_wf1$percent_flagged[4], 1)`% of the items were marked for DIF.

<br>

## By hf_1_parameter

### All Specs
```{r}
result_hf_1_all <- create_flagged_item_table(all_specifications, hf_1_correction)
result_hf_1_all
```

### No LR Specs
```{r}
result_hf_1_nolr <- create_flagged_item_table(nolr_specifications, hf_1_correction)
result_hf_1_nolr
```

### Double check with alternative process
```{r}
plotdata %>% 
  filter(yvar %in% correction) %>% 
  group_by(yvar) %>% 
  dplyr::summarise(times_flagged = sum(fill ==2)) %>%
  mutate(percent = times_flagged / (length(unique(plotdata$xvar))) *100)
```

## By hf_2_parameter

### All Specs
```{r}
result_hf_2_all <- create_flagged_item_table(all_specifications, hf_2_parameter_vector)
result_hf_2_all
```

### No LR

```{r}
result_hf_2_nolr <- create_flagged_item_table(nolr_specifications, hf_2_parameter_vector)
result_hf_2_nolr
```
#### Double check with alternative process
```{r}
plotdata %>% filter(yvar %in% parameters) %>% group_by(yvar) %>% dplyr::summarise(times_flagged = sum(fill ==2))  %>% 
  mutate(percent = times_flagged / (length(unique(plotdata$xvar))) *100)
```
### Text

```{r}
result_hf_2 <- result_hf_2_nolr
```

When analyzing `r result_hf_2$hf_2_parameter_vector[1]`, it was observed that `r round(result_hf_2$percent_flagged[1], 1)`% of all items were flagged for DIF. When using `r result_hf_2$hf_2_parameter_vector[2]`, `r round(result_hf_2$percent_flagged[2], 1)`% of all items were detected to have DIF.


## By hf_3_criterion

### All Specs
```{r}
result_hf_3_all <- create_flagged_item_table(all_specifications, hf_3_criterion) 

result_hf_3_percent_method_all <- result_hf_3_all %>% 
  mutate(method = case_when(
    str_detect(hf_3_criterion, "Cox") ~ "R2 Cox",
    str_detect(hf_3_criterion, "McFadden") ~ "R2 McFadden",
    str_detect(hf_3_criterion, "Nagelkerke") ~ "R2 Nagelkerke",
    str_detect(hf_3_criterion, "beta") ~ "beta",
    str_detect(hf_3_criterion, "lr") ~ "lr",
    TRUE ~ "other" # This will assign "other" to rows where none of the above conditions are TRUE. You can adjust as needed.
  )) %>% 
  dplyr::group_by(method) %>% 
  dplyr::summarise(sum = sum(sum)) %>% 
  dplyr::mutate(percent_flagged = sum / (nrow(all_specifications)*35) *100) # nrow(specifications) analyses by 35 potential item flags
result_hf_3_percent_method_all
```

### No LR
```{r}
result_hf_3_nolr <- create_flagged_item_table(nolr_specifications, hf_3_criterion) 

result_hf_3_percent_method_nolr <- result_hf_3_nolr %>% 
  mutate(method = case_when(
    str_detect(hf_3_criterion, "Cox") ~ "R2 Cox",
    str_detect(hf_3_criterion, "McFadden") ~ "R2 McFadden",
    str_detect(hf_3_criterion, "Nagelkerke") ~ "R2 Nagelkerke",
    str_detect(hf_3_criterion, "beta") ~ "beta",
    str_detect(hf_3_criterion, "lr") ~ "lr",
    TRUE ~ "other" # This will assign "other" to rows where none of the above conditions are TRUE. You can adjust as needed.
  )) %>% 
  dplyr::group_by(method) %>% 
  dplyr::summarise(sum = sum(sum)) %>% 
  dplyr::mutate(percent_flagged = sum / (nrow(nolr_specifications)*35) *100) # nrow(specifications) analyses by 35 potential item flags
result_hf_3_percent_method_nolr
```



## Table All Specs

```{r}
colnames(result_wf1_all)[1] <- "id"
colnames(result_hf_1_all)[1] <- "id"
colnames(result_hf_2_all)[1] <- "id"
colnames(result_hf_3_percent_method_all)[1] <- "id"

table_all_specs <- bind_rows(
  result_wf1_all,
  result_hf_1_all,
  result_hf_2_all,
  result_hf_3_percent_method_all)
```

## Table No LR Specs
```{r}
colnames(result_wf1_nolr)[1] <- "id"
colnames(result_hf_1_nolr)[1] <- "id"
colnames(result_hf_2_nolr)[1] <- "id"
colnames(result_hf_3_percent_method_nolr)[1] <- "id"

table_nolr <- bind_rows(
  result_wf1_nolr,
  result_hf_1_nolr,
  result_hf_2_nolr,
  result_hf_3_percent_method_nolr)

full_join(table_all_specs, table_nolr, by = "id") %>% 
  mutate(percent_flagged.x = round(percent_flagged.x, 1),
         percent_flagged.y = round(percent_flagged.y, 1),
         ) %>% 
  dplyr::select(Specification = id,
         "Items Flagged" = sum.x,
         "Flagged All Methods (%)" = percent_flagged.x,
         "Flagged LR Excluded (%)" = percent_flagged.y) 
  
```


# Figures: Amount of Flagged Items per DIF Analysis

## Setup
```{r}
data_flagged_items <- all_specifications %>%
  #filter(method != "lr") %>% 
  rowwise() %>% 
  dplyr::mutate(sum = sum(c_across(PFM1:PFM9))) %>%
  ungroup() %>%  
  mutate(
    wf_1_comparison = toupper(wf_1_comparison), # Convert to uppercase
    hf_1_correction = sapply(hf_1_correction, function(x) str_to_title(x)), # First letter uppercase for each word
    hf_2_parameter = case_when(
      hf_2_parameter == "parameters_promis" ~ "PROMIS",
      hf_2_parameter == "parameters_multigroup" ~ "Multigroup",
      TRUE ~ hf_2_parameter # Default case if there are other values
    ),
    hf_3_criterion = case_match(
      hf_3_criterion,
      "lr: 0.01"     ~ "LR: 0.01",
      "lr: 0.05"     ~ "LR: 0.05",
      "lr_bon: 0.01" ~ "LR Bonferroni: 0.01",
      "lr_bon: 0.05" ~ "LR Bonferroni: 0.05",
      "lr_ben: 0.01" ~ "LR BH: 0.01",
      "lr_ben: 0.05" ~ "LR BH: 0.05",
      .default =  hf_3_criterion # Default case if there are other values
    )
  )
data_flagged_items$hf_3_criterion = factor(data_flagged_items$hf_3_criterion, 
                                           levels = rev(c("CoxSnell: 0.02", 
                                                          "CoxSnell: 0.03", 
                                                          "CoxSnell: 0.05", 
                                                          "McFadden: 0.02", 
                                                          "McFadden: 0.03", 
                                                          "McFadden: 0.05",
                                                          "Nagelkerke: 0.02", 
                                                          "Nagelkerke: 0.03", 
                                                          "Nagelkerke: 0.05",
                                                          "Nagelkerke", 
                                                          "beta: 0.1",
                                                          "beta: 0.05",
                                                          "LR: 0.01",
                                                          "LR: 0.05",
                                                          "LR Bonferroni: 0.01",
                                                          "LR Bonferroni: 0.05",
                                                          "LR BH: 0.01",
                                                          "LR BH: 0.05")))
```

## Histogram
```{r}
hist_flagged_items <- data_flagged_items %>% 
  ggplot(aes(x = sum)) +
  geom_histogram(binwidth = 1, color = "black", fill = "#21918c") +
  theme_minimal() +
  labs(title = "Histogram: Amount of Flagged Items From Each DIF Analysis", 
       x = "Number of Flagged Items per Analysis", 
       y = "Frequency of Analyses")

hist_flagged_items
```

## Distribution
```{r}
p1 <- data_flagged_items %>%
  ggplot(aes(x = wf_1_comparison, y = sum, fill = wf_1_comparison)) +
  geom_boxplot(alpha = 0.5) +
    geom_jitter(alpha = 0.3) +
  scale_fill_viridis_d() +
  labs(title = "a) Specification: Country Comparison", x = "Country Comparison", y = "Number of Flagged Items") +
  theme_minimal() +
  theme(legend.position = "none") +
  coord_flip()

p2 <- data_flagged_items %>%
  ggplot(aes(x = hf_1_correction, y = sum, fill = hf_1_correction)) +
  geom_boxplot(alpha = 0.5) +
    geom_jitter(alpha = 0.3) +
  scale_fill_viridis_d() +
  labs(title = "b) Specification: Type of Correction", x = "Correction", y = "Number of Flagged Items") +
  theme_minimal() +
  theme(legend.position = "none") +
  coord_flip()

p3 <- data_flagged_items %>%
  ggplot(aes(x = hf_2_parameter, y = sum, fill = hf_2_parameter)) +
  geom_boxplot(alpha = 0.5) +
  geom_jitter(alpha = 0.3) +
  scale_fill_viridis_d() +
  labs(title = "c) Specification: Type of Item Parameters", x = "Item Parameters", y = "Number of Flagged Items") +
  theme_minimal() +
  theme(legend.position = "none") +
  coord_flip()

p4 <- data_flagged_items %>%
  ggplot(aes(x = hf_3_criterion, y = sum, fill = hf_3_criterion)) +
  geom_boxplot(alpha = 0.5) +
    geom_jitter(alpha = 0.3) +
  scale_fill_viridis_d() +
  labs(title = "d) Specification: DIF Flagging Criterion and Threshold", x = "Method", y = "Number of Flagged Items") +
  theme_minimal() +
  theme(legend.position = "none") +
  coord_flip()

combined_plot123 <- plot_grid(p1, p2, p3, ncol = 1, align = 'v')

combined_plot <- plot_grid(combined_plot123, p4, ncol = 2, align = 'v')

print(combined_plot)
```


```{r}
data_flagged_items %>%
    filter(wf_1_comparison == "") %>% 
    ggplot(aes(x = wf_1_comparison, y = sum, fill = wf_1_comparison)) +
    geom_boxplot(alpha = 0.5) +
    scale_fill_viridis_d() +
    labs(title = "Specification: Country Comparison", x = "Country Comparison", y = "Number of Flagged Items") +
    theme_minimal() +
    theme(legend.position = "none") +
    coord_flip()
```

```{r}
plot_filterd_multiverse <- function(variable, value) {
  
  p1 <- data_flagged_items %>%
    filter({{variable}} == value) %>% 
    ggplot(aes(x = wf_1_comparison, y = sum, fill = wf_1_comparison)) +
    geom_boxplot(alpha = 0.5) +
    scale_fill_viridis_d() +
    labs(title = "Specification: Country Comparison", x = "Country Comparison", y = "Number of Flagged Items") +
    theme_minimal() +
    theme(legend.position = "none") +
    coord_flip()
  
  p2 <- data_flagged_items %>%
    filter({{variable}} == value) %>% 
    ggplot(aes(x = hf_1_correction, y = sum, fill = hf_1_correction)) +
    geom_boxplot(alpha = 0.5) +
    scale_fill_viridis_d() +
    labs(title = "Specification: Type of Correction", x = "Correction", y = "Number of Flagged Items") +
    theme_minimal() +
    theme(legend.position = "none") +
    coord_flip()
  
  p3 <- data_flagged_items %>%
    filter({{variable}} == value) %>% 
    ggplot(aes(x = hf_2_parameter, y = sum, fill = hf_2_parameter)) +
    geom_boxplot(alpha = 0.5) +
    scale_fill_viridis_d() +
    labs(title = "Specification: Type of Item Parameters", x = "Item Parameters", y = "Number of Flagged Items") +
    theme_minimal() +
    theme(legend.position = "none") +
    coord_flip()
  
  p4 <- data_flagged_items %>%
    filter({{variable}} == value) %>% 
    ggplot(aes(x = hf_3_criterion, y = sum, fill = hf_3_criterion)) +
    geom_boxplot(alpha = 0.5) +
    scale_fill_viridis_d() +
    labs(title = "Specification: DIF Flagging Criterion and Threshold", x = "Method", y = "Number of Flagged Items") +
    theme_minimal() +
    theme(legend.position = "none") +
    coord_flip()
  
  combined_plot123 <- plot_grid(p1, p2, p3, ncol = 1, align = 'v')
  
  combined_plot <- plot_grid(combined_plot123, p4, ncol = 2, align = 'v')
  
  print(combined_plot)
  
}
```

```{r}
plot_filterd_multiverse(variable = wf_1_comparison, value = "USA-GER-ARG")
plot_filterd_multiverse(wf_1_comparison, "GER-ARG")
plot_filterd_multiverse(hf_1_correction, "Age")
```

