---
title: "Differential Item Functioning By Language on the new PROMIS® Physical Functioning Items 2.0 for Adults"
subtitile: "3.0 Analysis the DIF Multiverse: Setup"
author: "Constantin Yves Plessen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: show
    highlight: pygment
    keep_md: no
    theme: cerulean
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      collapse = FALSE,
                      comment = "",
                      strip.white = TRUE,
                      warning = FALSE, #we exclude warnings to improve readability
                      messages = FALSE,
                      lwd = 2,
                      out.width = "100%",
                      fig.width=10, 
                      fig.height=10,
                      fig.align = "center",
                      dpi = 300)

library(haven)
library(lordif)
body(plot.lordif)[[9]] <- NULL #https://stackoverflow.com/questions/52904512/r-lordif-rmarkdown

library(readxl)
library(arsenal) 
library(summarytools) 
library(hrbrthemes)
library(cowplot)
library(janitor)
library(car)
library(lavaan)
library(semPlot)
library(psych)
library(nFactors)
library(kableExtra)
library(doParallel)
library(gpttools)
library(plyr)
library(reshape)
library(mirt)
library(mirtCAT)
library(rms)
library(ggplot2)
library(MASS)
library(gridExtra)
library(pander)
library(raincloudplots)
library(dplyr)
library(tidyverse)
library(corrplot)

options(scipen = 999)

# Source helper functions
source("R/helper-functions.R")
source("R/estimate_parameters.R")
source("R/prepare_promis_parameters.R")
source("R/select_promis_parameters.R")
source("R/create_purified_model.R")
```


# Overview

This document creates a data frame from the multiverse results and adds baseline and corrected results to out

<br>

# 1. Setup

## Data for analyses

### Load data 
```{r}
### Primary Data 
load("data/data_complete.rda")

### Load data from analyses
load("data/specifications.RData") # original data used in publication
```

### Load and prepare item parameters

```{r}
pars <- read.csv("data/tidy/PROMIS_PF_parameters_pertubated.csv") # pertubated item parameters, cannot be shared and needs to be obtained from PROMIS

# All ceiling items
pf_items <- c("PFM1", "PFM2", "PFM3", "PFM4", "PFM6", "PFM7", "PFM9", "PFM10", 
              "PFM12", "PFM15", "PFM16", "PFM17", "PFM18", "PFM19", "PFM21", 
              "PFM23", "PFM25", "PFM26", "PFM27", "PFM28", "PFM29", "PFM32", 
              "PFM33", "PFM34", "PFM35", "PFM36", "PFM37", "PFM38", "PFM40", 
              "PFM43", "PFM44", "PFM46", "PFM49", "PFM51", "PFM53")

# remove non-ceiling items from data
data_clean <- data_complete %>% 
  mutate(sample_id = respondent_id) %>% 
  dplyr:: select(sample_id, country, age, all_of(pf_items)) 
```


## Data for item information

```{r}
data_items_spa <- read_excel("data/tidy/items_ao2.xlsx", sheet = 2)

data_items_ger <- read_excel("data/tidy/items_ao2.xlsx", sheet = 3)

data_items_eng <- read_excel("data/tidy/items_ao2.xlsx", sheet = 1) %>% 
  filter(id %in% data_items_ger$id)
```


## Selecting Data

```{r}
# create a vector of countries to filter the data by
grouping_vector <- c("usa", "ger", "arg")

# filter the data by the countries in the grouping vector
dat_usa_ger_arg <- filter_data(data_clean, 
                               countries = grouping_vector)

items_usa_ger_arg <- filter_items(data_clean, 
                                  countries = grouping_vector)

# create a vector of countries to filter the data by
grouping_vector <- c("usa", "ger")

# filter the data by the countries in the grouping vector
dat_usa_ger<- filter_data(data_clean, 
                          countries = grouping_vector)

items_usa_ger <- filter_items(data_clean, 
                              countries = grouping_vector)

# create a vector of countries to filter the data by
grouping_vector <- c("usa", "arg")

# filter the data by the countries in the grouping vector
dat_usa_arg <- filter_data(data_clean, 
                           countries = grouping_vector)

items_usa_arg <- filter_items(data_clean, 
                              countries = grouping_vector)

# create a vector of countries to filter the data by
grouping_vector <- c("ger", "arg")

# filter the data by the countries in the grouping vector
dat_ger_arg <- filter_data(data_clean, 
                           countries = grouping_vector)

items_ger_arg <- filter_items(data_clean, 
                              countries = grouping_vector)


```

<br>

# 2. Create data frame with results from multiverse analysis

Create data with information of which and how factors, and flagged items.
```{r}
specifications_results <- NULL

# Create data frame row of first iteration
specifications_results <- cbind(out[[1]]$specification, 
                                k_flagged = length(out[[1]]$results[[length(out[[1]]$results)]]$Flagged_items),
                                Flagged_items = paste0(out[[1]]$results[[length(out[[1]]$results)]]$Flagged_items, collapse = "-"))

# add the additional rows
for (i in 2:length(out)) {
  current_specifications <- cbind(out[[i]]$specification, 
                                  k_flagged = length(out[[i]]$results[[length(out[[i]]$results)]]$Flagged_items),
                                  Flagged_items = paste0(out[[i]]$results[[length(out[[i]]$results)]]$Flagged_items, collapse = "-"))
  specifications_results <- bind_rows(specifications_results, current_specifications)
}
```

# 3. Add alternative thetas to out

## Prepare PROMIS Parameters
```{r}
parameters_promis <- prepare_promis_parameters(pars = pars, 
                                               pf_items = pf_items, 
                                               data=dat_usa_ger_arg)
```

### Create baseline models
```{r}
grouping_vector <- c("usa", "ger", "arg")
param_usa_ger_arg_mgroup <- estimate_parameters(dat_usa_ger_arg, grouping_vector)
param_usa_ger_arg_promis <- select_promis_parameters(parameters_promis, grouping_vector)

param_usa_ger_arg_mgroup %>% filter(item == "GROUP")
param_usa_ger_arg_promis  %>% filter(item == "GROUP")
```


```{r}
grouping_vector <- c("usa", "ger")
param_usa_ger_mgroup <- estimate_parameters(dat_usa_ger, grouping_vector)
param_usa_ger_promis <- select_promis_parameters(parameters_promis, grouping_vector)
```


```{r}
grouping_vector <- c("usa", "arg")
param_usa_arg_mgroup <- estimate_parameters(dat_usa_arg, grouping_vector)
param_usa_arg_promis <- select_promis_parameters(parameters_promis, grouping_vector)
```


```{r}
grouping_vector <- c("ger", "arg")
param_ger_arg_mgroup <- estimate_parameters(dat_ger_arg, grouping_vector)
param_ger_arg_promis <- select_promis_parameters(parameters_promis, grouping_vector)
```


### `create_baseline_dataframes()`
```{r}
create_baseline_dataframes <- function(countries) {
  country_codes <- c("usa", "ger", "arg")
  
  if (!all(countries %in% country_codes)) {
    stop("Invalid country code(s). Please use 'usa', 'ger', or 'arg'.")
  }
  
  # Filter the data based on the input countries
  dat_filtered <- dat_usa_ger_arg %>%
    filter(country %in% countries)
  
  # Create group factor
  group <- factor(dat_filtered$country, levels = country_codes)
  
  # Create a string with the country codes concatenated by underscores
  country_str <- paste(countries, collapse = "_")
  
  # Select the correct parameters
  mgroup_params <- get(paste0("param_", country_str, "_mgroup"))
  promis_params <- get(paste0("param_", country_str, "_promis"))
  
  # Create the baseline dataframes
  assign(paste0("baseline_", country_str, "_mgroup"), 
         multipleGroup(dat_filtered[, -c(1:3)], 
                       group = group, 
                       model = 1, 
                       itemtype = "graded", 
                       pars = mgroup_params), 
         envir = .GlobalEnv)
  
  assign(paste0("baseline_", country_str, "_promis"), 
         multipleGroup(dat_filtered[, -c(1:3)], 
                       group = group, 
                       model = 1, 
                       itemtype = "graded", 
                       pars = promis_params), 
         envir = .GlobalEnv)
}

create_baseline_dataframes(c("usa", "ger", "arg"))
create_baseline_dataframes(c("ger", "arg"))
create_baseline_dataframes(c("usa", "arg"))
create_baseline_dataframes(c("usa", "ger"))
```


```{r}
# List of Baseline Models with Promis Parameters
baseline_models <- list(
  
  baseline_usa_ger_arg_mgroup = baseline_usa_ger_arg_mgroup, 
  baseline_usa_ger_arg_promis = baseline_usa_ger_arg_promis, 
  
  baseline_usa_ger_mgroup = baseline_usa_ger_mgroup, 
  baseline_usa_ger_promis = baseline_usa_ger_promis, 
  
  baseline_usa_arg_mgroup = baseline_usa_arg_mgroup, 
  baseline_usa_arg_promis = baseline_usa_arg_promis, 
  
  baseline_ger_arg_mgroup = baseline_ger_arg_mgroup, 
  baseline_ger_arg_promis = baseline_ger_arg_promis
)
```

## Add thetas and model for baseline models to out

```{r}
# Define a lookup table for the models
model_lookup <- list(
  'usa-ger-arg' = list(
    'parameters_multigroup' = baseline_models$baseline_usa_ger_arg_mgroup,
    'parameters_promis' = baseline_models$baseline_usa_ger_arg_promis
  ),
  'usa-ger' = list(
    'parameters_multigroup' = baseline_models$baseline_usa_ger_mgroup,
    'parameters_promis' = baseline_models$baseline_usa_ger_promis
  ),
  'ger-arg' = list(
    'parameters_multigroup' = baseline_models$baseline_ger_arg_mgroup,
    'parameters_promis' = baseline_models$baseline_ger_arg_promis
  ),
  'usa-arg' = list(
    'parameters_multigroup' = baseline_models$baseline_usa_arg_mgroup,
    'parameters_promis' = baseline_models$baseline_usa_arg_promis
  )
)
```

```{r}
# Function to get the model based on specification
get_model <- function(wf_1_comparison, hf_2_parameter_vector) {
  if (!wf_1_comparison %in% names(model_lookup)) {
    stop("Invalid wf_1_comparison")
  }
  models_for_comparison <- model_lookup[[wf_1_comparison]]
  if (!hf_2_parameter_vector %in% names(models_for_comparison)) {
    stop("Invalid hf_2_parameter_vector")
  }
  return(models_for_comparison[[hf_2_parameter_vector]])
}

# Function to create baseline_model list
create_baseline_model <- function(model) {
  theta_values <- fscores(model)
  return(list(
    model = model, # corrected model
    parameter = mod2values(model),
    thetas = theta_values,
    theta_se = fscores(model, full.scores.SE = TRUE)[, "SE_F1"] %>% as.vector(),
    ets = mirt::expected.test(model, Theta = theta_values, group = 1)
  ))
}

# Main loop
for (i in 1:length(out)) {
  wf_1_comparison <- as.character(out[[i]]$specification$wf_1_comparison)
  hf_2_parameter_vector <- out[[i]]$specification$hf_2_parameter_vector
  
  # Use the function to get the model
  mod <- get_model(wf_1_comparison, hf_2_parameter_vector)
  
  # Create baseline_model list
  out[[i]]$results_baseline <- create_baseline_model(mod)
  
  # Store the theta_baseline (for compatibility or other uses)
  out[[i]]$theta_baseline <- out[[i]]$results_baseline$thetas
}
```


```{r working-version}
#baseline <- list()
#
#for (i in 1:length(out)) {
#  switch(as.character(out[[i]]$specification$wf_1_comparison),
#         "usa-ger-arg" = {
#           if (out[[i]]$specification$hf_2_parameter_vector == "parameters_multigroup") {
#             baseline$mod <- baseline_models$baseline_usa_ger_arg_mgroup
#           } else if (out[[i]]$specification$hf_2_parameter_vector == "parameters_promis") {
#             baseline$mod <- baseline_models$baseline_usa_ger_arg_promis
#           } else {
#             stop("Invalid hf_2_parameter_vector")
#           }
#           out[[i]]$theta_baseline <- fscores(baseline$mod)
#           
#         },
#         "usa-ger" = {
#           if (out[[i]]$specification$hf_2_parameter_vector == "parameters_multigroup") {
#             baseline$mod <- baseline_models$baseline_usa_ger_mgroup
#           } else if (out[[i]]$specification$hf_2_parameter_vector == "parameters_promis") {
#             baseline$mod <- baseline_models$baseline_usa_ger_promis
#           } else {
#             stop("Invalid hf_2_parameter_vector")
#           }
#           out[[i]]$theta_baseline <- fscores(baseline$mod)
#           
#         },
#         "usa-arg" = {
#           if (out[[i]]$specification$hf_2_parameter_vector == "parameters_multigroup") {
#             baseline$mod <- baseline_models$baseline_usa_arg_mgroup
#           } else if (out[[i]]$specification$hf_2_parameter_vector == "parameters_promis") {
#             baseline$mod <- baseline_models$baseline_usa_arg_promis
#           } else {
#             stop("Invalid hf_2_parameter_vector")
#           }
#           out[[i]]$theta_baseline <- fscores(baseline$mod)
#           
#         },
#         "ger-arg" = {
#           if (out[[i]]$specification$hf_2_parameter_vector == "parameters_multigroup") {
#             baseline$mod <- baseline_models$baseline_ger_arg_mgroup
#           } else if (out[[i]]$specification$hf_2_parameter_vector == "parameters_promis") {
#             baseline$mod <- baseline_models$baseline_ger_arg_promis
#           } else {
#             stop("Invalid hf_2_parameter_vector")
#           }
#           out[[i]]$theta_baseline <- fscores(baseline$mod)
#           
#         },
#         {
#           stop("Invalid wf_1_comparison")
#         }
#  )
#}
```

## Add thetas from corrected models to out

### Add model
```{r}
out <- lapply(out, function(x) {
  x$results_corrected <- x$results[[length(x$results)]]$corrected_model
  return(x)
})
```

### Add thetas
```{r}
out <- lapply(out, function(x) {
  x$theta_corrected <- as.vector(fscores(x$results[[length(x$results)]]$corrected_model$model))
  return(x)
})
```



## Add thetas from purified models to out

```{r}
# Function to prepare data and parameters
prepare_data_and_params <- function(wf_1_comparison, hf_2_parameter_vector, flagged_items) {
  data <- get(paste0("dat_", gsub("-", "_", wf_1_comparison)))
  param_type <- ifelse(str_detect(hf_2_parameter_vector, "promis"), "promis", "mgroup")
  param <- get(paste0("param_", gsub("-", "_", wf_1_comparison), "_", param_type)) 
  param <- param %>% dplyr::filter(!item %in% flagged_items) %>% 
    dplyr::mutate(parnum = 1:nrow(.))
  return(list(data = data, param = param))
}

# Improved loop
for (i in 1:length(out)) {
  tryCatch({
    wf_1_comparison <- as.character(out[[i]]$specification$wf_1_comparison)
    hf_2_parameter_vector <- out[[i]]$specification$hf_2_parameter_vector
    flagged_items <- out[[i]]$results$`last iteration`$Flagged_items
    
    # Prepare data and parameters
    prep <- prepare_data_and_params(wf_1_comparison, hf_2_parameter_vector, flagged_items)
    
    # Run the model creation function
    out[[i]]$results_purified <- create_purified_model(
      prep$data, 
      unlist(strsplit(wf_1_comparison, "-")),
      hf_2_parameter_vector, 
      flagged_items, 
      prep$param)
    
    out[[i]]$theta_purified <- out[[i]]$results_purified$thetas
  }, 
  error = function(e) {
    # Error handling
    if(grepl("Too few degrees of freedom", e$message) || 
       grepl("Rows in supplied and starting value data.frame objects do not match", e$message) || 
       grepl("length of 'dimnames'", e$message)) {
      out[[i]]$theta_purified <- NA
    } else {
      stop(e)
    }
  })
}

```


```{r works}
#for (i in 1:length(out)) {
#  tryCatch(
#    {
#      wf_1_comparison <- as.character(out[[i]]$specification$wf_1_comparison)
#      hf_2_parameter_vector <- out[[i]]$specification$hf_2_parameter_vector
#      flagged_items <- out[[i]]$results$`last iteration`$Flagged_items
#      
#      if (str_detect(hf_2_parameter_vector, "promis")) {
#        # Select appropriate dataset and parameters based on comparison
#        data <- get(paste0("dat_", gsub("-", "_", wf_1_comparison)))
#        param <- get(paste0("param_", gsub("-", "_", wf_1_comparison), "_", "promis")) 
#        param <- param %>% filter(!item %in% flagged_items) %>% 
#          mutate(parnum = 1:nrow(.))
#        out[[i]]$results_purified <- create_purified_model(data, 
#                                                                          #unlist(strsplit(wf_1_comparison, "-")),
#                                                                          hf_2_parameter_vector, 
#                                                                          flagged_items, 
#                                                                          param)
#        out[[i]]$theta_purified <- out[[i]]$results_purified$thetas
#        
#      } else if(str_detect(hf_2_parameter_vector, "multigroup")){
#        # Select appropriate dataset and parameters based on comparison
#        data <- get(paste0("dat_", gsub("-", "_", wf_1_comparison)))
#        param <- get(paste0("param_", gsub("-", "_", wf_1_comparison), "_", "mgroup")) 
#        param <- param %>% filter(!item %in% flagged_items) %>% 
#          mutate(parnum = 1:nrow(.))
#        out[[i]]$results_purified <- create_purified_model(data, 
#                                                                          #unlist(strsplit(wf_1_comparison, "-")),
#                                                                          hf_2_parameter_vector, 
#                                                                          flagged_items, 
#                                                                          param)
#        out[[i]]$theta_purified <- out[[i]]$results_purified$thetas
#      }
#    },
#    error = function(e) {
#      if(grepl("Too few degrees of freedom", e$message) || 
#         grepl("Rows in supplied and starting value data.frame objects do not match", e$message) || 
#         grepl("length of 'dimnames'", e$message)) {
#        out[[i]]$theta_purified <- NA
#      } else {
#        stop(e)
#      }
#    }
#  )
#}


```

```{r working version}
#for (i in 1:length(out)) {
#  tryCatch(
#    {
#      wf_1_comparison <- as.character(out[[i]]$specification$wf_1_comparison)
#      hf_2_parameter_vector <- out[[i]]$specification$hf_2_parameter_vector
#      flagged_items <- out[[i]]$results$`last iteration`$Flagged_items
#      
#      if (str_detect(hf_2_parameter_vector, "promis")) {
#        # Select appropriate dataset and parameters based on comparison
#        data <- get(paste0("dat_", gsub("-", "_", wf_1_comparison)))
#        param <- get(paste0("param_", gsub("-", "_", wf_1_comparison), "_", "promis")) 
#        param <- param %>% filter(!item %in% flagged_items) %>% 
#          mutate(parnum = 1:nrow(.))
#        out[[i]]$theta_purified <- create_purified_model(data, 
#                                                         unlist(strsplit(wf_1_comparison, "-")),
#                                                         hf_2_parameter_vector, 
#                                                         flagged_items, 
#                                                         param)
#        
#      } else if(str_detect(hf_2_parameter_vector, "multigroup")){
#        # Select appropriate dataset and parameters based on comparison
#        data <- get(paste0("dat_", gsub("-", "_", wf_1_comparison)))
#        param <- get(paste0("param_", gsub("-", "_", wf_1_comparison), "_", "mgroup")) 
#        param <- param %>% filter(!item %in% flagged_items) %>% 
#          mutate(parnum = 1:nrow(.))
#        out[[i]]$theta_purified <- create_purified_model(data, 
#                                                         unlist(strsplit(wf_1_comparison, "-")),
#                                                         hf_2_parameter_vector, 
#                                                         flagged_items, 
#                                                         param)
#      }
#    },
#    error = function(e) {
#      if(grepl("Too few degrees of freedom", e$message) || 
#         grepl("Rows in supplied and starting value data.frame objects do not match", e$message) || 
#         grepl("length of 'dimnames'", e$message)) {
#        out[[i]]$theta_purified <- NA
#      } else {
#        stop(e)
#      }
#    }
#  )
#}
#
```

```{r}
for (i in seq_along(out)) {
  # Rename 'results' to 'analysis_results' if it exists
  if ("results" %in% names(out[[i]])) {
    names(out[[i]])[names(out[[i]]) == "results"] <- "analysis_results"
  }
  
  # Order the elements of each sublist based on the names
  out[[i]] <- out[[i]][order(names(out[[i]]))]
}
```


### Save out

```{r}
save(out, file = "data/results.RData")
```

